Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-08-18 manuscript/manuscript.tex
Minor changes in manuscript

The tests were performed on a thin and a thick spherical shell of 1 km and 35 km of thickness, respectively.
In Figures \ref{fig:D-linear-thin} and \ref{fig:D-linear-thick} we can see the results for the potential, the vertical component of the gradient and the $g_{zz}$ component of the Marussi tensor.
Because the other two diagonal components of the tensor show similar results as the ones obtained for the $g_{zz}$, we exclude them from the figure.
Although they can be found in the repository. \todo{chequear}

For the linear density case, we can observe that the calculation of the potential and the $g_z$ component of its gradient needs a value of $D=1$ and $D=2$, respectively, in order to ensure an accuracy of 0.1\%.
On the other hand, the $g_{zz}$ computations show a noticeable difference between the thin and the thick shell: the first one needs a value of $D=8$ while the later only a $D=3.5$.
We will keep the more conservative result of $D=8$ in case of computing the Marussi tensor components in case of a linear density tesseroid.

@@

\noindent where $A$ = 1kg/m$^3$ and $b$ = 1000km.
We have also performed this test with a thin and a thick shell of 1 km and 35 km, respectively, and the results can be seen in Figures \ref{fig:D-exp-thin} and \ref{fig:D-exp-thick}.
Once again, the results for $g_{xx}$ and $g_{yy}$ are very similar to the ones obtained for $g_{zz}$, so we exclude them. Although, they can be found in the repository.

>>>>

The tests were performed on a thin and a thick spherical shell of 1 km and 35 km of thickness, respectively.
In Figures \ref{fig:D-linear-thin} and \ref{fig:D-linear-thick} we can see the results for the potential, the vertical component of the gradient $g_z$ and the $g_{zz}$ component of the Marussi tensor.
Because the other two diagonal components of the tensor show similar results as the ones obtained for the $g_{zz}$, we exclude them from the figure, although they can be found in the repository. \todo{chequear}

For the linear density case, we can observe that the calculation of the potential and the $g_z$ component of its gradient needs a value of $D=1$ and $D=2$, respectively, in order to ensure an accuracy of 0.1\%.
On the other hand, the $g_{zz}$ computations show a noticeable difference between the thin and the thick shell: the first one needs a value of $D$ equal to 8 while the later only a $D$ of 3.5.
We will keep the more conservative result of $D$ equal to 8 in case of computing the Marussi tensor components in case of a linear density tesseroid.

@@

\noindent where $A$ = 1kg/m$^3$ and $b$ = 1000km.
We have also performed this test with a thin and a thick shell of 1 km and 35 km, respectively, and the results can be seen in Figures \ref{fig:D-exp-thin} and \ref{fig:D-exp-thick}.
Once again, the results for $g_{xx}$ and $g_{yy}$ are very similar to the ones obtained for $g_{zz}$, so we exclude them, although, they can be found in the repository.
